\cvsection{Selected Projects}
\begin{cventries}
  \cventry
    {Agriculture Hackathon held by government}
    {Agriblack}
    {Taipei, Taiwan}
    {Aug. 2016}
    {
      \begin{cvitems}
        \item {Created a website that allows users to record daily fruit users have taken and recognize the picture to analyze the nutrition.}
        \item {Gaming rules such as collecting badges, level upgrading, sending gift were involved.}
        \item{Got corporate sponsorship(GIGABYTE. Inc).}
        \item {{\color{red}\href{https://github.com/fifiteen82726/agriblack}{https://github.com/fifiteen82726/agriblack}}}
      \end{cvitems}
    }
  \cventry
  {Graduation Project}
    {Animal Killer}
    {Yuan Ze University}
    {July. 2013 - Dec. 2014}
    {
      \begin{cvitems}
        \item {Implemented a stable motion tracking system by using statistical mathematical model for Microsoft Kinect.}
        \item {Built with Unity3D and added gaming component, and participated Microsoft Image Cup and China Unity Adwards Competition.}
        \item{More detail: {\color{red}\href{https://www.slideshare.net/CodaChang1/animal-killer-82988561}{slideshare}}}
      \end{cvitems}
    }
  \cventry
  {Open Source Contribution}
    {ruby-http-client}
    {Github}
    {Oct. 2017}
    {
      \begin{cvitems}
        \item {Helped SendGrid build CI/CD and implement the API in Rbuy.}
        \item{{\color{red}\href{https://github.com/sendgrid/ruby-http-client}{https://github.com/sendgrid/ruby-http-client}}}
      \end{cvitems}
    }
\end{cventries}
\vspace{-\baselineskip}